Appendix

### 2022-01-07 paper/manuscript/appendix.Rmd
add goldset face/hand analysis and figure updates

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
theme_few(base_size=12) +
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
   theme_few(base_size=12) +
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

@@

@@

```{r}
ggplot(face_hand_by_age_milestones,
       aes(x=age_day_bin, y=prop,
           size=log10(num_frames_total),
           col=walking)) +
  geom_point(alpha=.3) +
  ylab('Proportion Detections') +
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(region ~ child_name) +
  theme_few(base_size=10) +
  viridis::scale_color_viridis(name = "", option="C", discrete=TRUE, begin=0, end=.4) +
  theme(legend.text=element_text(size=10)) +
  guides(size = FALSE) +
  theme(legend.position="right")

>>>>

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=12) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=12) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

@@

```{r}
summary_by_age_days_gold <- gold_sample %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(face_present_ketan), 
            num_hands = sum(hand_present_ketan), 
            num_detect = n()) %>%
  mutate(prop_faces = num_faces / num_detect, 
         prop_hands = num_hands / num_detect) %>%
  select(prop_faces, prop_hands, age_days, child_id) %>%
  pivot_longer(col = c(prop_faces, prop_hands), names_to="region", values_to = "prop")

summary_by_age_days_gold$age_scale <- scale(summary_by_age_days_gold$age_days, scale = FALSE)[,1] / 30.3
```

```{r}

## add face vs. hands model on gold sample to sanity check
diff_model2_gold <- summary(lmer(prop ~ region*poly(age_scale, 2) + (1 | child_id), data = summary_by_age_days_gold))

xtable(diff_model2_gold$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces and hands seen by infants based on human annotations.")

@@

```{r}
ggplot(face_hand_by_age_milestones,
       aes(x=age_day_bin, y=prop,
           size=log10(num_frames_total),
           col=walking)) +
  geom_point(alpha=.3) +
  ylab('Proportion Detections') +
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(region ~ child_name) +
  theme_few(base_size=10) +
  viridis::scale_color_viridis(name = "", option="C", discrete=TRUE, begin=0, end=.4) +
  theme(legend.text=element_text(size=10)) +
  guides(size = FALSE) +
  theme(legend.position="bottom")
